Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-25 stp/paper_aaai/main.tex
gotten a  bit of space left
Correct bib file and add new results

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Diego De Una , Natalia Rummele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Diego De U\~na$^1$ , Natalia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
$^1$Department of Computing and Information Systems --- The University of Melbourne\\
$^2$Siemens, Germany ~~~~~
$^3$Data61, CSIRO, Melbourne, Australia\\
d.deunagomez@student.unimelb.edu.au, nataliia.ruemmele@siemens.com\\ \{gkgange,schachte,pstuckey\}@unimelb.edu.au
}

@@

Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts.
%: schema matching and schema mapping.
First, \emph{semantic labeling} finds 
correspondences between attributes from data sources and data nodes of the 
target ontology.
Second, in the \emph{schema mapping} part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.

@@

\begin{table}[ht]\small
	\vspace*{-0.8em}
  \centering
  \caption{Description of data sources.\vspace*{-0.8em}}\label{tab:data}
		\begin{tabular}{ccccc}
		\hline
		\multirow{2}{*}{\textbf{Domain}} & \# data & \# semantic & \# & \# unknown\\
		 & sources & labels & attributes & attributes\\
		\hline
		museum & 29 & 20 & 443 & 159  \\
		soccer & 12 & 18 & 138 & 42 \\
		\hline
		\end{tabular} 
\end{table}
}

@@

\begin{table}[!ht]\small
  \centering 
  \vspace*{-0.8em}
  \caption{Average performance of semantic labeling models% for leave one out strategy.
  	  \vspace*{-0.8em}}
  	\label{tab:semlab}
  	\scalebox{0.8}{
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & 
  		\multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.560 & 0.618 & 156.6 & 36.3\\
 		\textsc{Serene(Pats)} & 0.866 & 0.827 & 100.6 & 6.80\\
  		\hline
		\end{tabular} 
		}
%\vspace*{-3mm}
\end{table}

@@

% karma vs serene vs serene-pats
We then evaluate \serene{} and \serenepats{} against the state-of-the-art system \karma{}.
All three systems have access to the same set of matches produced by our semantic labeling model.
Fig.~\ref{fig:perf} shows their performance on the museum and soccer domains.
We report average precision and recall for the systems with regard to variable 
number of semantic models in the training set.
For \serene{} and \serenepats{} we report the first solutions found by
\chuffed{}. All three systems find solutions in less than a second on average.
We use default parameters for \karma{} which were shown to yield the best 
results\forijcai{~\cite{taheriyan2016learning}}.
As we can see, \serene{} produces on average the best semantic models in terms 
of precision while \serenepats{} generates slightly better models in terms of 
recall.
The t-tests run for the obtained results confirm statistical significance of our improvements at the level $p<0.01$
%If we consider results separately per each instance and not on average, there 
%are few instances where \karma{} generates more precise models, however, our 
%new approaches produce much better models in terms of recall in all considered 
%instances. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% sequential solution
In Fig.~\ref{fig:loo} we show how the performance of \serene{} changes 
across sequentially found solutions.
\chuffed{}, the solver of \serene{}, successively finds better solutions in terms of Eq. \ref{EQ:obj}.
However,
that does not translate directly into more precise semantic models.
On average, we have observed that \serene{} yields very good results already 
with the first solution found, and plateaus after the third solution.
Also, we have explored how the systems perform if we manually filter out the unmatched attributes.
In such scenarios, \serene{} also yields better solutions than \karma{}, and can often prove optimality of the found solutions.
This observation provides further evidence of the validity of our new framework.

@@

\begin{table}[!ht]\small
  \centering
  \caption{Example table.}
  	\begin{tabular}{ccc} 
  		\hline
		Person & Age & Gender \\
  		\hline
	    John & 20 & M\\
    	Jane & 30 & F\\
  		\hline
		\end{tabular} 
%\vspace*{-3mm}
\end{table}

\begin{table}[h]
	\centering
	\caption{Feature extractors that produce a scalar value}
	\begin{tabular}{p{3cm}p{4.5cm}}
	Feature name & Description \\ \hline
	num-unique-vals & A simple count of unique entries of a column\\
	\rowcolor{Gray}
	prop-unique-vals & The proportion of unique entries of a column. \\
	\rowcolor{Gray}
	prop-missing-vals & The proportion of all missing/empty entries from all entries in a column.\\
	ratio-alpha-chars & The average of the proportion of alphabetic characters from each entry.\\
	\rowcolor{Gray}
	prop-numerical-chars & The average of the proportion of numeric characters from each entry.\\
	prop-whitespace-chars    & The average of the proportion of whitespace characters from each entry.\\
	\rowcolor{Gray}
	prop-entries-with-at-sign& The proportion of entries with an '@' sign. \\
	prop-entries-with-hyphen & The proportion of entries with a '-'. \\
	\rowcolor{Gray}
	prop-range-format        & The proportion of entries which follow some numerical range format   ([0-9]+)-([0-9]+) \\
	is-discrete              & A binary indicator if the column entries are discrete. \\
	\rowcolor{Gray}
	entropy-for-discrete-values & The entropy of the entries of a column.\\
	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
	\end{tabular}
\end{table}

>>>>

\pdfinfo{
/Title (Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping)
/Author (Diego De Una , Natalia Rummele, Graeme Gange, Peter Schachte and Peter J. Stuckey)
/Keywords (Machine Lerning Application, Constraint Programming, Ontology, Relational, Steiner Tree)}
\setcounter{secnumdepth}{2}  
 \begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping }
\author{Diego De U\~na$^1$ , Nataliia R\"ummele$^2$, Graeme Gange$^1$, Peter Schachte$^1$ \and Peter J. Stuckey$^{1,3}$\\
$^1$Department of Computing and Information Systems --- The University of Melbourne\\
$^2$Siemens, Germany ~~~~~
$^3$Data61, CSIRO, Melbourne, Australia\\
d.deunagomez@student.unimelb.edu.au, nataliia.ruemmele@siemens.com\\ \{gkgange,schachte,pstuckey\}@unimelb.edu.au
}

@@

Following the traditional data integration framework~\cite{doan2012principles}, we decompose the problem into two parts.
%: schema matching and schema mapping.
First, \emph{semantic labeling} \cite{ruemmele2018evaluating} finds 
correspondences between attributes from data sources and data nodes of the 
target ontology.
Second, in the \emph{schema mapping} part we want to generate the semantic models of data sources by identifying the connecting paths for the matched data nodes.

@@

\begin{table}[ht]\small
	\vspace*{-0.8em}
  \centering
  \caption{Description of data sources.\vspace*{-0.8em}}\label{tab:data}
		\begin{tabular}{ccccc}
		\hline
		\multirow{2}{*}{\textbf{Domain}} & \# data & \# semantic & \# & \# unknown\\
		 & sources & labels & attributes & attributes\\
		\hline
		museum & 29 & 20 & 443 & 159  \\
		soccer & 12 & 18 & 138 & 42 \\
		\hline
		\end{tabular} 
		\vspace*{-3em}
\end{table}
}

@@

\begin{table}[!ht]\small
  \centering 
  \vspace*{-0.8em}
  \caption{Average performance of semantic labeling models% for leave one out strategy.
  	  \vspace*{-0.8em}}
  	\label{tab:semlab}
  	\scalebox{0.8}{
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{MRR scores} & 
  		\multicolumn{2}{c}{Train time ($s$)}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		DSL & 0.560 & 0.618 & 156.6 & 36.3\\
 		\textsc{Serene(Pats)} & 0.866 & 0.827 & 100.6 & 6.80\\
  		\hline
		\end{tabular} 
		}
\vspace*{-3mm}
\end{table}

@@

% karma vs serene vs serene-pats
We then evaluate \serene{} and \serenepats{} against the state-of-the-art system \karma{}.
All three systems have access to the same set of matches produced by our semantic labeling model.
Fig.~\ref{fig:perf} shows their performance on the museum and soccer domains.
We report average precision and recall for the systems with regard to variable 
number of semantic models in the training set.
For \serene{} and \serenepats{} we report the first solutions found by
\chuffed{}. All three systems find solutions in less than a second on average.
We use default parameters for \karma{} which were shown to yield the best 
results\forijcai{~\cite{taheriyan2016learning}}.
As we can see, \serene{} produces on average the best semantic models in terms 
of precision while \serenepats{} generates slightly better models in terms of 
recall.
The t-tests run for the obtained results confirm statistical significance of our improvements at the level $p<0.01$
%If we consider results separately per each instance and not on average, there 
%are few instances where \karma{} generates more precise models, however, our 
%new approaches produce much better models in terms of recall in all considered 
%instances. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!ht]\small
  \centering 
  \vspace*{-0.8em}
  \caption{Performance with unknowns manually removed% for leave one out strategy.
  	  \vspace*{-0.8em}}
  	\label{tab:nounkn}
  	\scalebox{0.8}{
  	\begin{tabular}{c|cc|cc} 
  		\hline
  		\multirow{2}{*}{Model} & \multicolumn{2}{c|}{Precision} & 
  		\multicolumn{2}{c}{Recall}\\
  		 & museum & soccer & museum & soccer\\
  		\hline
  		\karma{} &  0.72 & 0.87 & 0.54 & 0.61 \\
 		\serene{} & 0.82 & 0.86 & 0.62 & 0.75 \\
		\serenepats{} & 0.6 & 0.86 & 0.64 & 0.75 \\  		
  		\hline
		\end{tabular} 
		}
\vspace*{-3mm}
\end{table}

%% sequential solution
In Fig.~\ref{fig:loo} we show how the performance of \serene{} changes 
across sequentially found solutions.
\chuffed{}, the solver of \serene{}, successively finds better solutions in terms of Eq. \ref{EQ:obj}.
However,
that does not translate directly into more precise semantic models.
On average, \serene{} yields very good results already 
with the first solution found, and plateaus after the third solution.
In Tab.~\ref{tab:nounkn} we show how the systems perform if we manually remove the unmatched attributes.
In such scenarios, \serene{} also yields better solutions than \karma{}, especially in terms of recall, and can often prove optimality of the found solutions.
This observation provides further evidence of the validity of our new framework.

@@

\begin{table}[!ht]\small
  \centering
  \caption{Example table.}
  	\begin{tabular}{ccc} 
  		\hline
		Person & Age & Gender \\
  		\hline
	    John & 20 & M\\
    	Jane & 30 & F\\
  		\hline
		\end{tabular} 
\vspace*{-3mm}
\end{table}

\begin{table}[h]
	\centering
	\caption{Feature extractors that produce a scalar value}
	\begin{tabular}{p{3cm}p{4.5cm}}
	Feature name & Description \\ \hline
	num-unique-vals & A simple count of unique entries of a column\\
	\rowcolor{Gray}
	prop-unique-vals & The proportion of unique entries of a column. \\
	\rowcolor{Gray}
	prop-missing-vals & The proportion of all missing/empty entries from all entries in a column.\\
	ratio-alpha-chars & The average of the proportion of alphabetic characters from each entry.\\
	\rowcolor{Gray}
	prop-numerical-chars & The average of the proportion of numeric characters from each entry.\\
	prop-whitespace-chars    & The average of the proportion of whitespace characters from each entry.\\
	\rowcolor{Gray}
	prop-entries-with-at-sign& The proportion of entries with an '@' sign. \\
	prop-entries-with-hyphen & The proportion of entries with a '-'. \\
	\rowcolor{Gray}
	prop-range-format        & The proportion of entries which follow some numerical range format   ([0-9]+)-([0-9]+) \\
	is-discrete              & A binary indicator if the column entries are discrete. \\
	\rowcolor{Gray}
	entropy-for-discrete-values & The entropy of the entries of a column.\\
	shannon-entropy          & Shannon's entropy for the vocabulary specified in the description of the feature 'char-dist-features'\\
	\end{tabular}
	\vspace*{-3mm}
\end{table}
